Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-16 tex/sections/consensus.tex
Fix a readability issue
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The reserve committee of delegates is able to fork the Argennon blockchain, if it receives a valid fork request
from the validators.
This fork needs to be confirmed by validators and can not discard more than one block that has been certified by
validators.
A valid fork request is an unexpired request signed by more than half of the total stake of validators.

@@

The emergency agreement protocol is a resilient protocol for deciding between a set of proposals when no committee of
delegates can be trusted. For initiating the protocol, a validator signs a message containing the subject
of the agreement and a start time.

>>>>

The reserve committee of delegates is able to fork the Argennon blockchain, if it receives a valid fork request
from validators.
A valid fork request is an unexpired request signed by more than half of the total stake of validators.

A fork created by the reserve committee needs to be confirmed by validators and can never discard more than one
block which has received a certificate from validators.

@@

The emergency agreement protocol is a resilient protocol for deciding between a set of proposals when the committee of
delegates is not available or can not be trusted. For initiating the protocol, a validator signs a message containing
the subject of the agreement and a start time.
